# Barrier Prioritization {-}

```{python}
#| echo: false
#| warning: false

import pandas as pd
import numpy as np
import warnings
import requests
import json
import pandas

def barrier_extent(barrier_type):

    request = 'https://cabd-pro.cwf-fcf.org/bcfishpass/functions/postgisftw.wcrp_barrier_extent/items.json?watershed_group_code=ELKR&barrier_type=' + barrier_type

    response_api = requests.get(request)
    parse = response_api.text
    result = json.loads(parse)

    blocked_km = result[0]['all_habitat_blocked_km']
    blocked_pct = result[0]['extent_pct']

    return blocked_km, blocked_pct

def barrier_count(barrier_type):
    request = 'https://cabd-pro.cwf-fcf.org/bcfishpass/functions/postgisftw.wcrp_barrier_count/items.json?watershed_group_code=ELKR&barrier_type=' + barrier_type

    response_api = requests.get(request)
    parse = response_api.text
    result = json.loads(parse)

    n_passable = result[0]['n_passable']
    n_barrier = result[0]['n_barrier']
    n_potential = result[0]['n_potential']
    n_unknown = result[0]['n_unknown']

    sum_bar = (n_passable, n_barrier, n_potential, n_unknown)

    return n_passable, n_barrier, n_potential, n_unknown, sum(sum_bar)

def barrier_severity(barrier_type):

    request = 'https://cabd-pro.cwf-fcf.org/bcfishpass/functions/postgisftw.wcrp_barrier_severity/items.json?watershed_group_code=ELKR&barrier_type=' + barrier_type

    response_api = requests.get(request)
    parse = response_api.text
    result = json.loads(parse)

    n_assessed_barrier = result[0]['n_assessed_barrier']
    n_assess_total = result[0]['n_assess_total']
    pct_assessed_barrier = result[0]['pct_assessed_barrier']

    return n_assessed_barrier, n_assess_total, pct_assessed_barrier

def watershed_connectivity(habitat_type):

    request = 'https://cabd-pro.cwf-fcf.org/bcfishpass/functions/postgisftw.wcrp_habitat_connectivity_status/items.json?watershed_group_code=ELKR&habitat_type=' + habitat_type

    response_api = requests.get(request)
    parse = response_api.text
    result = json.loads(parse)

    connect_stat = result[0]['connectivity_status']
    all_habitat = result[0]['all_habitat']
    all_habitat_acc = result[0]['all_habitat_accessible']

    return str(round(connect_stat)), all_habitat, all_habitat_acc

warnings.filterwarnings('ignore')

total = watershed_connectivity("ALL")[1] #total km in HORS
access = watershed_connectivity("ALL")[2]
gain = round((total*0.96)-access,2)
```

```{r}
#| echo: false
#| warning: false

library(reticulate)

gain <- py$gain

```

## Horsefly River Watershed Barrier Prioritization Summary {-}

The primary conservation outcome of the WCRP is the remediation of barriers to connectivity in the Elk River watershed. To achieve the 2041 connectivity goals in this plan (Goals 2 and 4), it is necessary to prioritize and identify a suite of barriers for both the Upstream of Elko Dam and Downstream of Elko Dam units that, if remediated, will provide access to a minimum of 142 km of habitat and 3 km of habitat, respectively (Table 12).


```{python echo=FALSE}
#| label: tbl-table16
#| tbl-cap: "Habitat connectivity gain requirements to meet WCRP goals in each WCRP unit of the Elk River watershed. The measures of currently accessible and total habitat values are derived from the Intrinsic Potential habitat model described in Appendix B."
#| warning: false
#| echo: false

import pandas as pd
import numpy as np
import matplotlib as mpl
import warnings

warnings.filterwarnings('ignore')

total = watershed_connectivity("ALL")[1] #total km in HORS
access = watershed_connectivity("ALL")[2]
gain = round((total*0.96)-access,2)

df = pd.DataFrame({"WCRP Unit":["Upstream of Elko Dam","Downstream of Elko Dam"],
                   "Currently accessible (km)":[str(access),"" ],
                   "Total": [str(total),  ""],
                   "Current Connectivity Status":[str(watershed_connectivity("ALL")[0])+"%", "" ],
                   "Goal": ["96%",""],
                   "Gain required (km)": [str(gain),  ""]
                   })

data = df.style.hide().set_properties(**{'text-align': 'left'})

data.set_table_styles(
   [{
       'selector': 'th',
       'props': [('background-color', '#008270'),('text-align', 'left')]
   }])

```

The barrier prioritization process comprises three stages:

- Stage 1: preliminary barrier list

- Stage 2: intermediate barrier list

- Stage 3: priority barrier list

The barrier prioritization analysis ranked barriers by the amount of habitat blocked to produce an "intermediate barrier list" comprising more barriers than are needed to achieve the goals. A longer list of barriers is needed due to the inherent assumptions in the connectivity model, habitat model, and gaps in available data. Barriers that have been modelled (i.e., points where streams and road/rail networks intersect) are assumed to be barriers until field verification is undertaken and structures that have been assessed as "potential" barriers (e.g., may be passable at certain flow levels or for certain life history stages) require further investigation before a definitive remediation decision is made.
Additionally, the habitat model identifies stream segmentsthat have the potential to support spawning or rearing habitat for target species but does not attempt to quantify habitat quality or suitability (see Appendix B), which will require additional field verification once barrier assessments have been completed. As such, the intermediate list of barriers (Table 14) should be considered as a starting point in the prioritization process and represents crossings that are a priority to evaluate further through barrier assessment and habitat confirmations because some structures will likely be passable, others will not be associated with usable habitat, some crossings may not exist, and others may not be feasible to remediate because of logistic considerations. The intermediate barrier list was updated following the barrier assessments and habitat confirmations that were undertaken during the 2021 field season - some barriers were moved forward to the "priority barrier list" (see Table 15) and others were eliminated from consideration due to one or more of the considerations discussed above (see Table 13). The priority barrier list represents structures that were confirmed to be partial or full barriers to fish passage and that block access to confirmed habitat.
Barriers on the priority list were reviewed by planning team members and selected for inclusion for proactive remediation. For more details on the barrier prioritization model, please see Mazany-Wright et al. 2021a.


```{r priority, echo = FALSE, results = 'asis'}
#| label: tbl-removed_above
#| tbl-cap: "List of barriers above Elko Dam that were prioritized as part of the first iteration of the intermediate barrier list (field assessments occurred during the 2021 field season) but were removed from consideration for proactive remediation following discussion with the planning team."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/removed-barriers-above.csv", check.names=FALSE)
prior_num <- length(data)
ft <- flextable(data) |> colformat_num(big.mark = "", decimal.mark = ".", digits = 2) 
ft <- bg(ft, bg = "#008270", part = "header")
ft <- color(ft, color = "white", part = "header")
ft <- set_caption(ft)
ft <- align_text_col(ft, align = "left", header = TRUE)
ft <- align_nottext_col(ft, align = "left", header = TRUE)
ft |> autofit() 
```

```{r deficient, echo = FALSE, results = 'asis'}
#| label: tbl-removed_below
#| tbl-cap: "List of barriers below Elko Dam that were prioritized as part of the first iteration of the intermediate barrier list (field assessments occurred during the 2021 field season) but were removed from consideration for proactive remediation following discussion with the planning team."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/removed-barriers-below.csv", check.names=FALSE)
inter_num <- length(data)
ft <- flextable(data) |> colformat_num(big.mark = "", decimal.mark = ".", digits = 2) 
ft <- bg(ft, bg = "#008270", part = "header")
ft <- color(ft, color = "white", part = "header")
ft <- set_caption(ft)
ft <- align_text_col(ft, align = "left", header = TRUE)
ft <- align_nottext_col(ft, align = "left", header = TRUE)
ft |> autofit() 
```

```{r intermediate_above, echo = FALSE, results = 'asis'}
#| label: tbl-intermediate_above
#| tbl-cap: "Intermediate barrier list resulting from barrier prioritization analysis in the Elk River watershed above Elko Dam. Crossings on this list have been identified as either potential barriers that require field verification or barriers/potential barriers that require further habitat investigations to determine their suitability as Westslope Cutthroat Trout habitat."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/intermediate-barriers-above.csv", check.names=FALSE)
inter_num <- length(data)
ft <- flextable(data) |> colformat_num(big.mark = "", decimal.mark = ".", digits = 2) 
ft <- bg(ft, bg = "#008270", part = "header")
ft <- color(ft, color = "white", part = "header")
ft <- set_caption(ft)
ft <- align_text_col(ft, align = "left", header = TRUE)
ft <- align_nottext_col(ft, align = "left", header = TRUE)
ft |> autofit() 
```


```{r intermediate_below, echo = FALSE, results = 'asis'}
#| label: tbl-intermediate_below
#| tbl-cap: "Intermediate barrier list resulting from barrier prioritization analysis in the Elk River watershed below Elko Dam. Crossings on this list have been identified as either potential barriers that require field verification or barriers/potential barriers that require further habitat investigations to determine their suitability as Westslope Cutthroat Trout habitat."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/intermediate-barriers-below.csv", check.names=FALSE)
inter_num <- length(data)
ft <- flextable(data) |> colformat_num(big.mark = "", decimal.mark = ".", digits = 2) 
ft <- bg(ft, bg = "#008270", part = "header")
ft <- color(ft, color = "white", part = "header")
ft <- set_caption(ft)
ft <- align_text_col(ft, align = "left", header = TRUE)
ft <- align_nottext_col(ft, align = "left", header = TRUE)
ft |> autofit() 
```


<!--
```{r fieldreq, echo = FALSE, results = 'asis'}
#| label: tbl-fieldreq
#| tbl-cap: "Field assessment requirements for the intermediate barrier list in the Horsefly River watershed. The cost per barrier values are estimates based on previously completed field work. The habitat confirmation count is based on the assumption that the 12 barriers requiring barrier assessments will also require a subsequent confirmation. In the case that some barriers are identified as unsuitable candidates for habitat confirmations, the total cost will be reduced."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/field-reqs.csv", check.names=FALSE)
ft <- flextable(data) 
ft <- bg(ft, bg = "#008270", part = "header")
ft <- color(ft, color = "white", part = "header")
ft <- set_caption(ft)
ft <- align_text_col(ft, align = "left", header = TRUE)
ft <- align_nottext_col(ft, align = "left", header = TRUE)
ft |> autofit() 
```
-->

There are currently `r prior_num` barriers on the priority barrier list, which will be pursued for proactive remediation to achieve the connectivity goals in this plan:

<!--
```{r remcost, echo = FALSE, results = 'asis'}
#| label: tbl-remcost
#| tbl-cap: "Preliminary barrier remediation cost estimate to reach connectivity goals in the Horsefly River watershed. Cost per barrier values are estimated based on the average cost of previously completed projects. Barrier counts and total costs are subject to change as more information is collected through the implementation of this plan."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/remediation-cost.csv", check.names=FALSE)
ft <- flextable(data)
ft <- bg(ft, bg = "#008270", part = "header")
ft <- color(ft, color = "white", part = "header")
ft <- set_caption(ft)
ft <- align_text_col(ft, align = "left", header = TRUE)
ft <- align_nottext_col(ft, align = "left", header = TRUE)
ft |> autofit() 
```
-->

```{r rehab, echo = FALSE, results = 'asis'}
#| label: tbl-priority
#| tbl-cap: "Elk River watershed priority barrier list, which includes barriers that have undergone field assessment, been reviewed by the planning team, and selected for proactive remediation. (Note that at present there are no priority barriers Below Elko Dam)."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/priority_structures_table.csv", check.names=FALSE)
ft <- flextable(data)
ft <- bg(ft, bg = "#008270", part = "header")
ft <- color(ft, color = "white", part = "header")
ft <- set_caption(ft)
ft <- align_text_col(ft, align = "left", header = TRUE)
ft <- align_nottext_col(ft, align = "left", header = TRUE)
ft |> autofit() 
```