```{r}
#| echo: false
#| warning: false

library(reticulate)
api <- import("python.api_calls")
gain <- api$gain

source("Rscripts/table_formatting.R")

```

# Data Download and Methods {-}

## Data Download {-}

Coming soon

## Connectivity Status Assessment Methods {-}

The connectivity status assessment for Westslope Cutthroat Trout in the Elk River watershed builds on existing connectivity modelling work undertaken by the BC Fish Passage Technical Working Group, resulting in a flexible, customizable open-source spatial model called ["bcfishpass"](https://github.com/smnorris/bcfishpass). The model spatially locates known and modelled barriers to fish passage, identifies potential spawning and rearing habitat for Westslope Cutthroat Trout, and estimates the amount of habitat that is currently accessible as part of the Longest Fragment for each WCRP unit. The Longest Fragment approach is adapted from @Diaz2021 and is calculated as the ratio between the length of largest connected set of habitat patches and the total length of all habitat patches in each WCRP unit. In the Elk River watershed, the longest fragment represents the mainstem Elk River and all currently connected tributaries, both upstream and downstream of the Elko Dam. As such, meeting the connectivity goals set in this plan requires prioritizing barriers for rehabilitaton that will reconnect tributaries to the existing longest fragments see [barrier prioritzation](barrier-prioritization.qmd).

The model uses an adapted version of the Intrinsic Potential (IP) fish habitat modelling framework (see @Sheer2009-kb for an overview of the IP framework). The habitat model uses two geomorphic characteristics of the stream network — channel gradient and mean annual discharge — to identify potential spawning habitat and rearing habitat for focal species. For the purposes of this plan, rearing habitat is used as an umbrella term to capture the requirements for Westslope Cutthroat Trout rearing, maintenance, and overwintering habitat. The habitat model does not attempt to definitively map each habitat type nor estimate habitat quality, but rather identifies stream segments that have high potential to support spawning or rearing habitat for Westslope Cutthroat Trout based on the geomorphic characteristics of the segment. For more details on the connectivity and habitat model structure and parameters, please see @Mazany-Wright2021-rz. The variables and thresholds used to model potential spawning and rearing habitat are summarized below. The quantity of modelled habitat was aggregated for each habitat type to inform the two KEAs — Accessible Habitat Upstream of Elko Dam and Accessible Habitat Downstream of Elko Dam — and represents a linear measure of potential habitat. To recognize the rearing value provided by features represented by polygons (e.g., lakes for overwintering) a multiplier of 1.5x the length of the stream segments flowing through the polygons was applied.

```{r, echo = FALSE, results = 'asis'}
#| label: tbl-param
#| tbl-cap: "Parameters and thresholds used to inform the Intrinsic Potential habitat model for spawning and rearing habitat for Westslope Cutthroat Trout in the Elk River watershed."
#| warning: false


data <- read.csv("data/params-elk.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

[References: [1] @Magee1996. [2] @Peterson2008. [3] @Bennett. [4] @Cosewic2016-qf.]{style="color: grey"}

## Other tables {-}

```{r, echo = FALSE, results = 'asis'}
#| label: tbl-nonaction
#| tbl-cap: "Non-Actionable structres"
#| warning: false


data <- read.csv("data/nonactionable_barriers.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r, echo = FALSE, results = 'asis'}
#| label: tbl-excluded
#| tbl-cap: "Excluded structures"
#| warning: false


data <- read.csv("data/excluded_structures.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```